Eurovision Song Contest: semifinal 1, 2009

### 2021-02-01 inst/eurovision.Rmd
inst/eurovision.Rmd

---
title: "Eurovision Song Contest: semifinal 1, 2009"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library("hyper2")
library("magrittr")
abbreviated <- TRUE  # change to FALSE for full names
```

## The Eurovision Song contest

The dataset `wiki_matrix`, defined below, is copied from "Eurovision
Song Contest 2009," Wikipedia, accessed May 13, 2018.  It refers to
semi-final 1.  More documentation is given in `eurovision.Rd` [type
`help(euro2009)` at the `R` prompt].

@@

```{r, specifymatrix}
data(eurovision)
(wiki_matrix <- as.matrix(eurovision2009_votingtable))
```

@@

```{r,prefsetter}
preference <- wiki_matrix*0  
for(i in seq_along(points)){ preference[wiki_matrix == points[i]] <- i }

@@

rownames(wiki_matrix) <- jj[1:18]
colnames(wiki_matrix) <- jj
```

@@

We need to convert matrix `preference` into a likelihood function,
here `eurovision2009`:

```{r,morestuff}
eurovision2009 <- hyper2()

for(i in seq_len(ncol(preference))){   # cycle through the rows; each row is a voter
    d <- preference[,i,drop=TRUE]
	eurovision2009 <- 	eurovision2009  + ordervec2supp(d[!is.na(d)])
} # i loop closes
```

@@

```{r,checknull,cache=TRUE}
m <- maxp(eurovision2009)
m
equalp.test(eurovision2009)
```

@@

```{r,orderplot}
points_scored <- rowSums(wiki_matrix,na.rm=TRUE)  # points
ox <- rank(-points_scored)
oy <- rank(-m)   # m = MLE
oyp <- ordertrans(oy,names(ox))

@@

>>>>

---
title: "Eurovision Song Contest: semifinal 1, 2009"
output: bookdown::html_document2
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library("hyper2")
library("magrittr")
options("digits" = 5)
abbreviated <- TRUE  # change to FALSE for full names
```

The file `eurovision.txt`, defined below, is copied from "Eurovision
Song Contest 2009," Wikipedia, accessed May 13, 2018.  It refers to
semi-final 1.  More documentation is given in `eurovision.Rd` [type
`help(euro2009)` at the `R` prompt].

@@

```{r, specifymatrix}
eurovision_table <- as.matrix(read.table("eurovision.txt"))
eurovision_table
```

@@

```{r,prefsetter}
preference <- eurovision_table*0  
for(i in seq_along(points)){ preference[eurovision_table == points[i]] <- i }

@@

rownames(eurovision_table) <- jj[1:18]
colnames(eurovision_table) <- jj
```

@@

We need to convert matrix `preference` into a likelihood function,
here `eurovision`:

```{r,morestuff}
eurovision <- hyper2()

for(i in seq_len(ncol(preference))){   # cycle through the rows; each row is a voter
    d <- preference[,i,drop=TRUE]
	eurovision <- eurovision + ordervec2supp(d[!is.na(d)])
} # i loop closes
```

```{r,checknull,cache=TRUE}
eurovision_maxp <- maxp(eurovision)
eurovision_maxp
```

```{r,plotpieeurovision,fig.cap="Maximum likelihood strengths of competitors in the 2009 Eurovision song contest, semifinal 1"} 
pie(eurovision_maxp)
```

@@

'''{r,label=equalptesteurovision,cache=TRUE}
equalp.test(eurovision)
```

@@

```{r,orderplot}
points_scored <- rowSums(eurovision_table,na.rm=TRUE)  # points
ox <- rank(-points_scored)
oy <- rank(-eurovision_maxp)   # m = MLE
oyp <- ordertrans(oy,names(ox))

@@

### Package dataset {-}

Following lines create `eurovision.rda`, residing in the `data/` directory of the package.

```{r,label=saveeurovisiondataset}
save(eurovision_table,eurovision_maxp,eurovision,file="eurovision.rda")
```
